---
title: "Lmwithpredictions"
author: "Adesuwa Mukoro"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
This is the linear model with prediction problem.
Predict strength scores using data from the following website. 


```{r}
dataF <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
```
```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
require(ggplot)
```

###Plot scatterplot

```{r}
plot(SIMS~ARM,data=dataF)
```

```{r}
basicNN <- ggplot(dataF,aes(y=SIMS,x=ARM))
basicNN + geom_point()+ geom_smooth(method=lm)
```

## now add the model fit to our plot

```{r}
model.1 <- lm(SIMS~ARM,data=dataF)
summary.lm(model.1)
New= data.frame(GRIP=94,ARM=88)
predict.lm(model.1,New,interval = "prediction")
```
Model 1 fit, the adjusted r-square is 0.467. About 47% of the variability in SIMS can be explained by the variability in ARM. The predicted score for SIMS is 0.71. The 95% confidence interval is from -1.726209 to 3.138977.


```{r}
model.2 <- lm(SIMS~GRIP,data=dataF)
summary.lm(model.2)
New= data.frame(GRIP=94,ARM=88)
predict.lm(model.2,New,interval = "prediction")
```

Model 2 fit,the adjusted R-square is 0.4053. About 41% of the variability in SIMS can be explained by the variability in GRIP. The predicted score in SIMS is -0.54. The 95% confidence interval is  from -3.167961 to 2.035652.

```{r}
model.3 <- lm(SIMS~ARM + GRIP,data=dataF)
summary.lm(model.3)
New= data.frame(GRIP=94,ARM=88)
predict.lm(model.3,New,interval = "prediction")
```

Model 3 fit, the adjusted R-square is 0.5358. About 54% of the variability in SIMS can be explained by the variability in both ARM and GRP. The predicted score in SIMS is 0.15. The 95% confident interval score is from -2.132373 to 2.431668.

```{r}
anova(model.1,model.3)
```

## Conclution

The anova compares model 1 and model 3. The P-value is 00000499, so we reject the null hypothesis. Both of these models are trying to predict SIMS. The null hypothesis about these models would be that there is no difference in either model predicting. The alternative hypothesis is that there is a difference because one model is better than the other. 
